---
title: "Conrad Borchers CV"
date: "Updated `r Sys.Date()`"
output:
  pagedown::html_paged:
    self_contained: false
    css: [borchers-cv.css]
    number_sections: false
links-to-footnotes: false
knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
library(dplyr)
```


```{r download-button, echo=FALSE, results='asis'}

include_dl_button <- F

if (include_dl_button) {
  cat(
    "
<div class = \"download\">
  Download PDF
  <a href=\"https://github.com/conradborchers/borchers-cv/raw/master/borchers-cv.pdf\" class=\"icon-block\">
  <i class=\"fas fafooter fa-download\"></i>
  </a>
</div>
    "
  )
}

```

<div id = "block_container">
<div class = "first", id="bloc1">Conrad</div>  
<div class = "last", id="bloc2">Borchers</div>
</div>

<p align="center">
<span style="color: #454545"><i class="fas fa-globe"></i></span> 
[cborchers.com](https://www.cborchers.com)
<span style="color: #454545; margin-left: 0.5em"><i class="fab fa-github"></i></span> [conradborchers](https://github.com/conradborchers/)
<span style="color: #454545; margin-left: 0.5em"><i class="fas fa-envelope"></i></span> 
conrad.borchers\@oii.ox.ac.uk
</p>

## Education

<p>
2021 --- 2022 <strong>Social Data Science M.Sc.</strong> - University of Oxford<br>
2018 --- 2021 <strong>Psychology B.Sc.</strong> - University of Tübingen, GPA: <strong>3.66</strong>/4.00
<br>
<p style="margin-left:40px">
<strong>Relevant Coursework:</strong> Inferential statistics, categorical data analysis,
experimental design and causal inference, psychometrics, multivariate statistics,
media and educational psychology, memory and learning
</p>

## Selected Work Experience

<strong>University of California, Berkeley - Graduate School of Education</strong><br>
<em>Research Intern, CAHL Lab of Prof. Zachary Pardos (May 2021 to September 2021)</em><br>
<ul>
<li>Co-authored a research article integrating psychological constructs, survey research, and machine learning research
</li><li>Led feature engineering of learning management system and enrollment data in Python
</li><li>Conducted mixed modeling of students’ time load and psychological stress in Python
</li>
</ul>

<strong>University of Tübingen - Hector Research Institute of Education Sciences</strong><br>
<em>Research Intern and Affiliate, Lab of Prof. Christian Fischer (Feb 2020 to present)</em><br>
<ul>
<li>Wrote downloading pipelines in shell script for the APIs of Twitter and CrowdTangle
</li><li>Applied and validated classification algorithms in Python on Twitter profiles
</li><li>Built data pipelines in R-targets to optimize the analysis of Twitter data sets
</li><li>Built SQLite databases combining Facebook data and public NCES school data
</ul>

## Fellowships and Honours

<strong>German National Merit Scholar (Studienstiftung)</strong><span style="float:right;">Awarded November 2018</span>
<br>
<strong>EFPSA Research Program Scholar</strong><span style="float:right;">2019/2020 Cohort</span>
<br>
<strong>Schmidt Futures Scholar (Learning Engineering, EPIC@Berkeley)</strong><span style="float:right;">Initial Cohort 2021</span>

## Selected Publications

<style>
.hangingindent {
  padding-left: 28px ;
  text-indent: -28px ;
} 
</style>

<p class="hangingindent">
Burchfield, M., Rosenberg, J., <strong>Borchers, C.</strong>, Thomas, T., Gibbons, B., & Fischer, C. (2021). Investigating the Privacy of Students’ Images and Names in the Context of K-12 Educational Institution’s Posts on Facebook. Proceedings of the 14th International Conference on Educational Data Mining (EDM). Paris, France. <strong>Best Poster Award.</strong> [[pdf](https://educationaldatamining.org/EDM2021/virtual/static/pdf/EDM21_paper_276.pdf)]
</p>

<p class="hangingindent">
Rosenberg, J., <strong>Borchers, C.</strong>, Dyer, E., Anderson, D. & Fischer, C. (2021). Understanding Public Sentiment About Educational 
	Reforms: The Next Generation Science Standards on Twitter. AERA Open, 7(1), 1-17. [[pdf]](https://journals.sagepub.com/doi/pdf/10.1177/23328584211024261)
</p>

## Skills

<strong>Skills:</strong> 
R (tidyverse, tidymodels, targets), Python (pandas, sklearn, NLTK), Bash, SPSS, SQL
<br>

<p><small>
```{r results = "asis", echo = FALSE}
cat("Updated", Sys.Date() %>% as.character())
```
</small></p>
