---
title: "Conrad Borchers CV"
date: "Updated `r Sys.Date()`"
output:
  pagedown::html_paged:
    self_contained: false
    css: [borchers-cv.css]
    number_sections: false
links-to-footnotes: false
knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
library(dplyr)
```


```{r download-button, echo=FALSE, results='asis'}

include_dl_button <- TRUE

if (include_dl_button) {
  cat(
    "
<div class = \"download\">
  Download PDF
  <a href=\"https://github.com/conradborchers/borchers-cv/raw/master/borchers-cv.pdf\" class=\"icon-block\">
  <i class=\"fas fafooter fa-download\"></i>
  </a>
</div>
    "
  )
}

```

<div id = "block_container">
<div class = "first", id="bloc1">Conrad</div>  
<div class = "last", id="bloc2">Borchers</div>
</div>

<p align="center">
<span style="color: #454545"><i class="fas fa-globe"></i></span> 
[cborchers.com](https://www.cborchers.com)
<span style="color: #454545; margin-left: 0.5em"><i class="fab fa-github"></i></span> [conradborchers](https://github.com/conradborchers/)
<span style="color: #454545; margin-left: 0.5em"><i class="fas fa-envelope"></i></span> 
conrad.borchers\@student.uni-tuebingen.de 
</p>

## Education

<p>
2018 --- 2021 <strong>Psychology B.Sc.</strong>, University of Tübingen, GPA: <strong>3.64</strong>/4.00
<br>
<p style="margin-left:40px">
<strong>Relevant Coursework:</strong> Inferential statistics, categorical data analysis,
experimental design and causal inference, psychometrics, multivariate statistics,
media and educational psychology, memory and learning
</p>

## Selected Work Experience

<strong>Hector Research Institute of Education Sciences</strong><br>
<em>Research Assistant and Intern, Lab of Prof. Christian Fischer (Feb 2020 to present)</em><br>
<ul>
<li>Wrote downloading pipelines in shell script for the APIs of Twitter and CrowdTangle
</li><li>Applied and validated classification algorithms in Python on Twitter profiles
</li><li>Built data pipelines in R-targets to optimize computation and storage of Twitter datasets
</li><li>Built SQLite databases combining Facebook data and public data of schools
</ul>

<strong>Leibniz Knowledge Media Center (IWM) and Tübingen School of Education</strong><br>
<em>Research Assistant, TabletBW Project on Tablet Use in K-12 Education (Feb 2019 to Jan 2021)</em><br>
<ul>
<li>Led final aggregation of students' and teachers' data across cohorts (SPSS, R)
</li><li>Improved participant ID matching and recovery through Python scripts 
</li><li>Supervised and maintained online teacher surveys in Unipark
</ul>

## Fellowships and Honours


<strong>German National Merit Scholar (Studienstiftung)</strong><span style="float:right;">Awarded November 2018</span>
<br>
<strong>EFPSA Research Programme Scholar</strong><span style="float:right;">2019/2020 Cohort</span>
<br>
<strong>Schmidt Futures Scholar (Learning Engineering, EPIC@Berkeley)</strong><span style="float:right;">Initial Cohort 2021</span>

## Selected Publications

<style>
.hangingindent {
  padding-left: 28px ;
  text-indent: -28px ;
} 
</style>

<p class="hangingindent">
 <strong>Borchers, C.</strong>, Eder, T. F., Scheiter, K. (preregistration). How Effective is Reflective Search? A Time Slice Analysis of Dentistry Students’ Visual Search Strategies and Pupil Dilation during the Diagnosis of Radiographs. PsychArchives. 
[[pdf]](https://hdl.handle.net/20.500.12034/4035)
</p>

<p class="hangingindent">
Rosenberg, J., <strong>Borchers, C.</strong>, Dyer, E., Anderson, D. & Fischer, C. (preprint). Advancing new methods for understanding public sentiment about 
educational reforms: The case of Twitter and the Next Generation Science Standards. OSF.
[[pdf]](https://osf.io/xymsd)
</p>

## Skills

<strong>Skills:</strong> 
R (tidyverse, markdown, shiny, targets), Python (pandas, sklearn, numpy, matplotlib), Bash, HTML, JavaScript, CSS, LaTeX, SPSS, SQL, C++

<br>

<p><small>
```{r results = "asis", echo = FALSE}
cat("Updated", Sys.Date() %>% as.character())
```
</small></p>
